---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# themedeltares

<!-- badges: start -->
<!-- badges: end -->

The goal of themedeltares is to add a new custom theme for ggplots in R. The theme is based on the Deltares corporate identity, including style and colours.

## Installation

You can install the development version of themedeltares from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("KeesWesdorp/theme_deltares")
```

## Example deltares_theme()

This is a basic example which shows you how to add the theme to your plots.
First we will obtain some sample data and create a standard ggplot.

```{r example}
library(themedeltares)

# obtaining some sample data
mtcars2 <- within(mtcars, {
   vs <- factor(vs, labels = c("V-shaped", "Straight"))
   am <- factor(am, labels = c("Automatic", "Manual"))
   cyl  <- factor(cyl)
   gear <- factor(gear)
 })


# creating a ggplot
 p1 <- ggplot2::ggplot(mtcars2) +
  ggplot2::geom_point(ggplot2::aes(x = wt, y = mpg, colour = gear)) +
   ggplot2::labs(
     title = "Fuel economy declines as weight increases",
     subtitle = "(1973-74)",
     caption = "Data from the 1974 Motor Trend US magazine.",
     tag = "Figure 1",
     x = "Weight (1000 lbs)",
     y = "Fuel economy (mpg)",
     colour = "Gears"
   )

# Adding the deltares theme
 p1 + theme_deltares() # the default

# adding the deltares theme when faceting
 p2 <- p1 + ggplot2::facet_grid(vs ~ am)
 p2 + theme_deltares()

```

## deltares_colors()

All available colors
```{r , echo =FALSE}
library(knitr)

lookup_table <- dplyr::tribble(
  ~color, ~hexcode,
  'zwart', '#000000',
  'blauw1', '#080c80',
  'blauw2', '#0d38e0',
  'blauw3', '#0ebbf0',
  'groen1', '#00b389',
  'groen2', '#00cc96',
  'groen3', '#00e6a1',
  'grijs1', '#f2f2f2',
  'grijs2', '#e6e6e6',
  'geel', '#ffd814',
  'academy', '#ff960d',
)

kable(lookup_table)
```

List of available colorschemes

* DeltaresDefault   = c('blauw1', 'blauw2', 'blauw3', 'groen1', 'groen2', 'groen3')
* DeltaresFull      = c('blauw1', 'blauw2', 'blauw3', 'groen1', 'groen2', 'groen3', 'academy', 'geel', 'grijs2', 'zwart')
* DeltaresBlues     = c('blauw1', 'blauw2', 'blauw3')
* DeltaresBlues_r   = c('blauw3', 'blauw2', 'blauw1')
* DeltaresGreens    = c('groen1', 'groen2', 'groen3')
* DeltaresGreens_r  = c('groen3', 'groen2', 'groen1')
* DeltaresOranges   = c('academy', 'geel', 'grijs2')
* DeltaresOranges_r = c('grijs2', 'geel', 'academy')

## examples of usages

```{r example 2}
library(themedeltares)

 deltares_colors() # default color scheme with 6 Deltares colours
 deltares_colors(colorscheme = "DeltaresFull") # all Deltares colours (n = 10)
 deltares_colors(palette = "sequential", ncolors = 10) # creates sequential color scheme with 10 colors starting with default color "blauw1" (#080c80) all the way to white (#FFFFFF)
 deltares_colors(palette = "sequential", color = "blauw3", shade = "dark", ncolors = 8)  # creates sequential scheme from      blauw3(#0ebbf0) to black (#000000)

 # Use with ggplot:

 library(ggplot2)


# create dataset
 mtcars2 <- within(mtcars, {
   vs <- factor(vs, labels = c("V-shaped", "Straight"))
   am <- factor(am, labels = c("Automatic", "Manual"))
   cyl  <- factor(cyl)
   carb <- factor(carb)
 })

 # create ggplot
  p1 <- ggplot2::ggplot(mtcars2) +
  ggplot2::geom_point(ggplot2::aes(x = wt, y = mpg, colour = carb)) +
   ggplot2::labs(
     title = "Fuel economy declines as weight increases",
     subtitle = "(1973-74)",
     caption = "Data from the 1974 Motor Trend US magazine.",
     tag = "Figure 1",
     x = "Weight (1000 lbs)",
     y = "Fuel economy (mpg)",
     colour = "Gears"
   )

 p1 + ggplot2::scale_colour_manual(values=c(deltares_colors())) # the default Deltares colourscheme

 # or in combination with deltares_theme()
 
 p1 + theme_deltares() + ggplot2::scale_colour_manual(values=c(deltares_colors()))
```
